\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-04-20 doc/incertae_sedis.tex
restoring \
Fix last undefined reference.

\subsection{Split-based semantics for emph{incertae sedis} taxa}

@@

The addition of \emph{incertae sedis} taxa allows new types of
conflict between input trees.
For example, different input trees might
place an incertae sedis taxon in conflicting locations.
This is
illustrated in Figure \ref{fig :placement-example1}, where the IS
taxon (ott7,ott6)ott10 is placed as sister to ott1 by phylogeny
$\tau_{1}$ and as sister ott3 by phylogeny $\tau_{2}$.

@@

\subsubsection{Exclude sets modified by emph{incertae sedis} marks}

>>>>

\subsection{Split-based semantics for \emph{incertae sedis} taxa}

@@

The addition of \emph{incertae sedis} taxa allows new types of
conflict between input trees.
For example, different input trees might
place an incertae sedis taxon in conflicting locations.
This is
illustrated in Figure \ref{fig:placement-example1}, where the IS
taxon (ott7,ott6)ott10 is placed as sister to ott1 by phylogeny
$\tau_{1}$ and as sister ott3 by phylogeny $\tau_{2}$.

@@

\subsubsection{Exclude sets modified by \emph{incertae sedis} marks}
